CAT-DWAM, A Question Answering System

### 2011-05-07 paper/paper.tex
edited paper.tex

@@

\subsection{Other choices}
Since the system was taking too long to run we made several choices in order
to get meaningful results on which to report on. We decided to specifically analyze
the "Where" questions since there were 28 of them, which seemed like an appropriate
amount on which to train on.

>>>>

To speed alignment (which runs in $O(mn)$ where m and n are the length of the strings being aligned, and the documents are several thousand characters), we cached previous alignments, and looked them up by the first 50 bytes of the two strings being aligned.  We also stored this in a file so that we could use the pre-computed values between runs.

@@

\subsection{Other choices}
Since the system was taking too long to run we made several choices in order
to get meaningful results on which to report on. We decided to specifically analyze
the "Where" questions since there were 28 of them, which seemed like an appropriate
amount which to train on.
